Estimation below the detection limit

### 2018-04-12 TEX/draft2.tex
About to do changes to 1D code to match moment sign conventions of the paper

For the purpose of this paper, we need the first three (aperiodic) autocorrelation functions. The first-order autocorelation is the mean of the signals. For  
$z\in\RL$ and $k\geq 2$, the higher order autocorrelations are defined by
\begin{equation} \label{eq:ac_general}
a_z^k[\ell_1,\ldots,\ell_{k-1}] =  \sum_{i=0}^{L-1-\max\{\ell_1,\ldots,\ell_{k-1}\}} z[i]z[i+\ell_1]\ldots z[i+\ell_{k-1}].
\end{equation}
Explicitly, the first three autocorrelations are
\begin{align} \label{eq:autocorrelations}
a_z^1 &= \sum_{i=0}^{L-1} z[i], \nonumber\\
a_z^2[\ell] &= \sum_{i=0}^{L-1-\ell} z[i]z[i+\ell], \nonumber\\
a_z^3[\ell_1,\ell_2] &= \sum_{i=0}^{L-1-\max\{\ell_1,\ell_2\}} z[i]z[i+\ell_1]z[i+\ell_2]. 
\end{align}
Note that the autocorrelation functions are symmetric so that $a_z^2[\ell] = a_z^2[-\ell]$ and $a_z^3[\ell_1,\ell_2] = a_z^3[-\ell_1,-\ell_2]$. \TODO{We also have $a_z^3[\ell_1,\ell_2] = a_z^3[\ell_2,\ell_1]$ -- is that intended? Do we really have symmetry with the negative signs? I think we have $(\ell_1, \ell_2) \sim (-\ell_1, \ell_2-\ell_1)$}
Additionally, if the moments of the signal depend only on the difference between the indices (Toeplitz structure), then they are equivalent to the autocorrelation functions.

@@

Given the observation $y$, we proceed to compute the moments. The first-order moment is straightforward. For second-order moments, notice from equation~\eqref{eq:data_ac} that $a_y^2[\ell]$ suffers no bias for $\ell$ in $1$ to $L-1$. Thus, we omit $\ell = 0$, which has the practical effect that we need not know $\sigma$ to estimate the moments. Likewise, for third-order moments, $a_y^3[\ell_1, \ell_2]$ for $0 \leq \ell_1, \ell_2 \leq L-1$ such that $\ell_1 + \ell_2 \leq L_1$ includes all relevant moments for our purpose, and we exclude any such that $\ell_1, \ell_2$ or $\ell_1 - \ell_2$ are zero to avoid biased elements. As a result, it is unnecessary to estimate $\sigma$. In practice, the moments are computed on batches of $y$ of length $100\cdot10^6$ and added up, without correction for the junction points. Batches are handled sequentially on a GPU, as GPUs are particularly well suited to execute simple instructions across large vectors of data.

>>>>

For the purpose of this paper, we need the first three (aperiodic) autocorrelation functions. The first-order autocorelation is the mean of the signals. For  
$z\in\RL$ and $k\geq 2$, the higher order autocorrelations are defined by
\begin{equation} \label{eq:ac_general}
a_z^k[\ell_1,\ldots,\ell_{k-1}] =  \sum_{i=0}^{L-1-\max\{\ell_1,\ldots,\ell_{k-1}\}} z[i]z[i+\ell_1]\ldots z[i+\ell_{k-1}].
\end{equation}
Explicitly, the first three autocorrelations are
\begin{align} \label{eq:autocorrelations}
a_z^1 &= \sum_{i=0}^{L-1} z[i], \nonumber\\
a_z^2[\ell] &= \sum_{i=0}^{L-1-\ell} z[i]z[i+\ell], \nonumber\\
a_z^3[\ell_1,\ell_2] &= \sum_{i=0}^{L-1-\max\{\ell_1,\ell_2\}} z[i]z[i+\ell_1]z[i+\ell_2]. 
\end{align}
Note that the autocorrelation functions are symmetric so that $a_z^2[\ell] = a_z^2[-\ell]$ and $a_z^3[\ell_1,\ell_2] = a_z^3[-\ell_1,-\ell_2]$. \TODO{We also have $a_z^3[\ell_1,\ell_2] = a_z^3[\ell_2,\ell_1]$ -- is that intended? Do we really have symmetry with the negative signs? I think we have $(\ell_1, \ell_2) \sim (-\ell_1, \ell_2-\ell_1)$; to be checked, but I don't think this is correct;}
Additionally, if the moments of the signal depend only on the difference between the indices (Toeplitz structure), then they are equivalent to the autocorrelation functions.

@@

Given the observation $y$, we proceed to compute the moments. The first-order moment is straightforward. For second-order moments, notice from equation~\eqref{eq:data_ac} that $a_y^2[\ell]$ suffers no bias for $\ell$ in $1$ to $L-1$. Thus, we omit $\ell = 0$, which has the practical effect that we need not know $\sigma$ to estimate the moments. Likewise, for third-order moments, $a_y^3[\ell_1, \ell_2]$ for $0 \leq \ell_1, \ell_2 \leq L-1$ such that $\ell_2 \leq \ell_1$ includes all relevant moments for our purpose \TODO{Do we want to include a figure to explain why that is?}, and we exclude any such that $\ell_1, \ell_2$ or $\ell_1 - \ell_2$ are zero to avoid biased elements. As a result, it is unnecessary to estimate $\sigma$. In practice, the moments are computed on batches of $y$ of length $100\cdot10^6$ and added up, without correction for the junction points. Batches are handled sequentially on a GPU, as GPUs are particularly well suited to execute simple instructions across large vectors of data.
